%# -*- coding: utf-8-unix -*-
% !TEX program = xelatex
% !TEX root = ../thesis.tex

\begin{thanks}

    First, I would like to express my sincere gratitude to Prof. Yong Yu,
    the program director of ACM Honors Class.
    I got to know Prof. Yong Yu in my second year of high school
    when I attended the summer school of ACM Honors Class.
    Back then, I was participating in Chinese National Olympiad in Informatics.
    The summer school helped me entered Shanghai Jiao Tong University,
    one of China's top universities, without much pressure on the college entrance examination.

    During the four years of my bachelor study,
    Prof. Yong Yu's philosophy on good conducts has been deeply influencing me.
    He is a man of decency, setting himself an example to students.
    He told us to learn to be a decent person before learning to do academic.
    He required us to act as a grown-up and be responsible for ourselves.
    Prof. Yong Yu has been improving university computer science education for decades.
    Whenever speaking of great impacts that graduated students of ACM Honors Class has made,
    I can see his face reflects happiness and pride.
    And when it comes to the gap between ACM Honors Class and the top schools in the world,
    he would look very distressed.
    It was him who made me believe that there are people who love education from heart
    and truly concerns about the future of the nation.
    I feel so lucky that I can learn from him.
    I believe Prof. Yong Yu's philosophy will deeply help me in my future life.

    Second, I want to thank Prof. Weinan Zhang, my advisor at the APEX Lab.
    Weinan gave me lots of advice on this thesis.
    When I was stuck, I went to talk to him.
    The discussion usually lasted no longer than five minutes.
    He is so experienced in machine learning that he could analysis the problems
    and give effective suggestions in such a short time,
    which saved me days of struggle if not weeks.
    I would not be able to finish this thesis without his advice.
    Weinan joined Shanghai Jiao Tong University as an assistant professor two years ago.
    Hence, I am one of first batch of students advised by him.
    I sincerely wish him a successful academic career.

    Third, I felt really happy to have a half-year internship at Cornell University.
    I would like to show my great respect and appreciation to my internship mentor Prof. Emin Gün Sirer.
    His charming personality attracted me, making me want to be a man like him.
    He has very decent research tastes, dealing with hard-core problems in systems area,
    which influenced me in such a short period of time as well.
    I would like to thank Ph.D. students at the Systems Lab: Ted Yin, Kai Mast, Soumya Basu, and Ayush Dubey.
    They showed great hospitality to me
    and helped me a lot with the research and the application to graduate schools.
    I also want to thank my roommates at Ithaca: Xueyuan Zhao and Yunqi Li.
    Their tolerance and encouragement kept me motivated on improving my cooking skill.

    Moreover, I am grateful to my classmates in ACM Honors Class.
    We had fun together. We faced failures together. And we fought together.
    We are like a family.

    Last but not least, I am very grateful to my parents for their unconditional support during these years.
    Without them, I cannot imagine how I could smoothly finish my undergraduate study.

    

\end{thanks}
